The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-18 paper/main.tex
paper: wordsmith, add box

\documentclass[12pt,modern]{aastex61}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{grffile} % checks for multiple dots in figure filenames

@@

A group of binarity-ignoring astronomers wants to measure the mean number of 
planets of a certain type per star of a certain type.
They perform a wide-field photometric search for planets that transit, and 
discover all for which
\begin{equation}
\left(\frac{{\rm S}}{{\rm N}}\right)
= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
\label{eq:S_N_thresh}
\end{equation}
The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
S}$. The survey is shot-noise dominated, and so the noise ${\rm N}$
scales as the inverse root of the photon flux received from any stellar 
system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ the 
system luminosity and $d$ its distance.
The solid angle coverage, telescope area, and survey duration are part of the 
``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
affects detectability, but we omit it in this work for brevity.

@@

\paragraph{On completeness}
Our expressions for the apparent rate density 
(Eqs.~\ref{eq:defn_apparent_rate_density} 
and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
detection efficiency.
If we were to take a smooth detection probability in S/N, we would need to 
include an explicit detection efficiency term in 
Eq.~\ref{eq:defn_apparent_rate_density} is to inversely weight for planets 
that had low probabilities of being detected.
However, our ``detection probability'' is a step function in S/N 
(Eq.~\ref{eq:S_N_thresh}).
In our model, the maximum searchable distance is only a function of the 
apparent depth and true system luminosity.
Even though the observers are selecting stars based on what they think are 
``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
actual searchability of a point-source is determined by apparent radius and 
system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
Fig.~\ref{fig:model_1_volumes}).
Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
searchable are exactly the stars that are selected, since dilution affects the 
apparent radius and the maximum searchable distance in equal and opposite 
order.

@@

\paragraph{General formula for apparent occurrence rate}
Using the results above, the apparent rate density,
\begin{align}
\Gamma\a(r\a,M\a) &= 
\frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
\sum_i n_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma^0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over 
    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
    \mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.
\label{eq:general_Gamma_a}
\end{align}
This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 
and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to create 
Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4}, 
and~\ref{fig:gaussian_HJ}.
It is validated in limits in which it is possible to write down the answer 
(e.g., Eq.~\ref{eq:model_1_apparent_rate_density}), and also against a Monte 
Carlo realization of the twin binary models (Secs.~\ref{sec:model_1} 
and~\ref{sec:model_2}).

>>>>

\documentclass[12pt,modern]{aastex61}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{grffile} % checks for multiple dots in figure filenames
\usepackage{empheq} % for boxing equations
\newcommand*\widefbox[1]{\fbox{\hspace{1em}#1\hspace{1em}}}

@@

A group of binarity-ignoring astronomers wants to measure the mean number of 
planets of a certain type per star of a certain type.
They perform a wide-field photometric search for planets that transit, and 
discover all for which
\begin{equation}
\left(\frac{{\rm S}}{{\rm N}}\right)
= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
\label{eq:S_N_thresh}
\end{equation}
The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
S}$. The survey is shot-noise dominated, and the fractional photon noise 
${\rm N}$ scales as the inverse root of the photon flux received from any 
stellar system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ 
the system luminosity and $d$ its distance.
The solid angle coverage, telescope area, and survey duration are part of the 
``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
affects detectability, but we omit it in this work for brevity.

@@

\paragraph{On completeness}
Our expressions for the apparent rate density 
(Eqs.~\ref{eq:defn_apparent_rate_density} 
and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
detection efficiency.
If we were to take a smooth detection probability in S/N, we would need to 
include an explicit detection efficiency term in 
Eq.~\ref{eq:defn_apparent_rate_density} to inversely weight for planets 
that had low probabilities of being detected.
However, our ``detection probability'' is a step function in S/N 
(Eq.~\ref{eq:S_N_thresh}).
In our model, the maximum searchable distance is only a function of the 
apparent depth and true system luminosity.
Even though the observers are selecting stars based on what they think are 
``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
actual searchability of a point-source is determined by apparent radius and 
system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
Fig.~\ref{fig:model_1_volumes}).
Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
searchable are exactly the stars that are selected, since dilution affects the 
apparent radius and the maximum searchable distance in equal and opposite 
order.

@@

\paragraph{General formula for apparent occurrence rate}
Using the results above, the apparent rate density,
\begin{align}
\Gamma\a(r\a,M\a) &= 
\frac{1}{N_{\rm s,a}(r\a,M\a) p_{\rm tra}(r\a,M\a)} \times
\sum_i n_{\rm det}^i (r\a,M\a),
\end{align}
evaluates to

\begin{empheq}[box=\widefbox]{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma^0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int {\mathrm{d}q \over \mathcal{A}^4}\,f(q)\,\Gamma^1\left({r\a\over 
    \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int {q \mathrm{d}q \over 
    {\mathcal{A}^3\mathcal{B}}}\,f(q)\,\Gamma^2\left({r\a\over 
    \mathcal{B}}, 
qM\a\right)\,
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\}.
\label{eq:general_Gamma_a}
\end{empheq}
This equation is used to derive Eqs.~\ref{eq:model5_apparent_rate_density} 
and~\ref{eq:powerlaw_vary_binary}, and is numerically integrated to create 
Figs.~\ref{fig:occ_rate_model_3_log},~\ref{fig:model_4}, 
and~\ref{fig:gaussian_HJ}.
It is validated in limits in which it is possible to write down the answer 
(e.g., Eq.~\ref{eq:model_1_apparent_rate_density}), and also against a Monte 
Carlo realization of the twin binary models (Secs.~\ref{sec:model_1} 
and~\ref{sec:model_2}).
